Network Configuration Synthesis with Abstract Topologies

### 2016-11-08 paper/abstraction/appendix.tex
add formal definitions

@@

  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     ma   &::=& n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3) & \textit{match action} \\
     ps   &::=& \{ t_1, ~\dots,~ t_k \} & \textit{predicates} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
  \end{array} \]%

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k) ) = \\
     ~~~~~ \{ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
     \\
     \textbf{compile}( p_1, \dots, p_k ) = \\
     ~~~~~~ compile_{ABGP}(compile_{PG}(p_1), \dots, compile_{PG}(p_k)) \\
  \end{array} \]%

  \end{minipage}

@@

  \caption{BGP syntax and compilation.}
  \label{fig:abgp-syntax}
\end{figure}%

@@

\[ \begin{array}{lcl}
  con(\emptyset,\Gamma,f)                        & = & \emptyset \\
  con(l,\Gamma,f)                                & = & \Sigma ~ f^{-1}(l) \\
  con(r_1 \cup r_2,\Gamma,f)                     & = & con(r_1,\Gamma,f) \cup con(r_2,\Gamma,f) \\
  con(r_1 \cap r_2,\Gamma,f)                     & = & con(r_1,\Gamma,f) \cap con(r_2,\Gamma,f) \\
  con(!r,\Gamma,f)                               & = & !con(r,\Gamma,f) \\
  con(r^*,\Gamma,f)                              & = & con(r,\Gamma,f)^* \\
  con(pfx \Rightarrow r_1, \dots, r_k,\Gamma,f)  & = & pfx \Rightarrow con(r_1,\Gamma,f), \dots, con(r_k,\Gamma,f) \\
  con(\$x \Rightarrow r_1, \dots, r_k,\Gamma,f)  & = & 
       \{ pfx \Rightarrow con(r_1,\Gamma,f) \cap \text{end}(l), 
          \dots, 
          con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \} \\
  %& & ~~~~~~~~~~~~~~~ \dots, \\
  %& & ~~~~~~~~~~~~~~~ con(r_k,\Gamma,G) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x),  ~l \in G.V \} \\
  con(p_1, \dots, p_n, \Gamma, f)                & = & con(p_1,\Gamma,f), \dots, con(p_n,\Gamma,f) \\
\end{array} \]

@@

\[ \begin{array}{lcl}
     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G) 
        & = & 
        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
        \\
     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G) 
        & = &  
        con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
        \\
     con(pfx \rightarrow {pc},\ell,\Gamma,f,G) 
        & = &  
        pfx \rightarrow con(pc,\text{true},\ell,\Gamma,f,G)
        \\
     con(\$x \rightarrow {pc},\ell,\Gamma,f,G) 
        & = &  
        \{ pfx \rightarrow con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
        \\
     con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G) 
        & = &
        con(ma_1,o,\ell,\Gamma,f,G), \dots, con(ma_k,o,\ell,\Gamma,f,G)
        \\

     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G) 
        & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
        &   & \textbf{else}~ n_1 : ( con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (con({ns}_2,\ell,\Gamma,f,G),n_3)

        \\
     con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G) 
        & = &  
        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
        \\
\end{array} \]

>>>>

\newcommand{\Con}{\text{con}}

@@

  \begin{minipage}[t]{.46\linewidth}
  \hdr{ABGP Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     ma   &::=& n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3) & \textit{match action} \\
     ps   &::=& \{ t_1, ~\dots,~ t_k \} & \textit{predicates} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
  \end{array} \]%

  \end{minipage}
  %
  %
  \begin{minipage}[t]{.5\linewidth}
  \hdr{Compilation}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k) ) = \\
     ~~~~~ \{ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
     \\
     \text{compile}( p_1, \dots, p_k ) = \\
     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1), \dots, \text{compile}_\text{PG}(p_k)) \\
  \end{array} \]%
  \end{minipage}

  \vspace{1em}
  \vspace{1em}

  \begin{minipage}[t]{\linewidth}
  \hdr{ABGP Concretization}{}
  \vspace*{-2\baselineskip}
  %
  \[ \begin{array}{lcl}
     \\
     \Con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G) 
        & = & 
        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
        \\
     \Con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G) 
        & = &  
        \Con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, \Con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
        \\
     \Con(pfx \rightarrow {pc},\ell,\Gamma,f,G) 
        & = &  
        pfx \rightarrow \Con(pc,\text{true},\ell,\Gamma,f,G)
        \\
     \Con(\$x \rightarrow {pc},\ell,\Gamma,f,G) 
        & = &  
        \{ pfx \rightarrow \Con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
        \\
     \Con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G) 
        & = &
        \Con(ma_1,o,\ell,\Gamma,f,G), \dots, \Con(ma_k,o,\ell,\Gamma,f,G)
        \\

     \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G) 
        & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
        &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)

        \\
     \Con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G) 
        & = &  
        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
        \\
  \end{array} \]%
  \end{minipage}

  \vspace{1em}
  \vspace{1em}

  \begin{minipage}[t]{\linewidth}
  \hdr{Policy Concretization}{}
  \vspace*{-2\baselineskip}
  %
  \[ \begin{array}{lcl}
     \\
     \Con(\emptyset, \Gamma, f)      &=& \emptyset \\
     \Con(l, \Gamma, f)              &=& \Sigma ~ f^{-1}(l) \\
     \Con(r_1 \cup r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cup \Con(r_2,\Gamma,f) \\
     \Con(r_1 \cap r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cap \Con(r_2,\Gamma,f) \\
     \Con(!r, \Gamma, f)             &=& !\Con(r,\Gamma,f) \\
     \Con(r^*, \Gamma, f)            &=& \Con(r,\Gamma,f)^* \\

     \Con(pfx ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=& 
          pfx ~\Path~ \Con(r_1,\Gamma,f), ~\dots~, \Con(r_k,\Gamma,f)  \\

     \Con(\$x ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&

         \{ pfx ~\Path~ \Con(r_1,\Gamma,f) \cap \text{end}(l), ~\dots~,
           \Con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \}  \\

     \Con(p_1, \dots, p_n, \Gamma,f) &=& \Con(p_1, \Gamma,f), \dots, \Con(p_n, \Gamma,f) \\

  \end{array} \]%
  \end{minipage}

@@

  \caption{BGP syntax and compilation and concretization.}
  \label{fig:abgp-syntax}

\end{figure}%

@@

%\[ \begin{array}{lcl}
%  con(\emptyset,\Gamma,f)                        & = & \emptyset \\
%  con(l,\Gamma,f)                                & = & \Sigma ~ f^{-1}(l) \\
%  con(r_1 \cup r_2,\Gamma,f)                     & = & con(r_1,\Gamma,f) \cup con(r_2,\Gamma,f) \\
%  con(r_1 \cap r_2,\Gamma,f)                     & = & con(r_1,\Gamma,f) \cap con(r_2,\Gamma,f) \\
%  con(!r,\Gamma,f)                               & = & !con(r,\Gamma,f) \\
%  con(r^*,\Gamma,f)                              & = & con(r,\Gamma,f)^* \\
%  con(pfx \Rightarrow r_1, \dots, r_k,\Gamma,f)  & = & pfx \Rightarrow con(r_1,\Gamma,f), \dots, con(r_k,\Gamma,f) \\
%  con(\$x \Rightarrow r_1, \dots, r_k,\Gamma,f)  & = & 
%       \{ pfx \Rightarrow con(r_1,\Gamma,f) \cap \text{end}(l), 
%          \dots, 
%          con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \} \\
%  %& & ~~~~~~~~~~~~~~~ \dots, \\
%  %& & ~~~~~~~~~~~~~~~ con(r_k,\Gamma,G) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x),  ~l \in G.V \} \\
%  con(p_1, \dots, p_n, \Gamma, f)                & = & con(p_1,\Gamma,f), \dots, con(p_n,\Gamma,f) \\
%\end{array} \]

@@

%\[ \begin{array}{lcl}
%     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G) 
%        & = & 
%        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
%        \\
%     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G) 
%        & = &  
%        con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
%        \\
%     con(pfx \rightarrow {pc},\ell,\Gamma,f,G) 
%        & = &  
%        pfx \rightarrow con(pc,\text{true},\ell,\Gamma,f,G)
%        \\
%     con(\$x \rightarrow {pc},\ell,\Gamma,f,G) 
%        & = &  
%        \{ pfx \rightarrow con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
%        \\
%     con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G) 
%        & = &
%        con(ma_1,o,\ell,\Gamma,f,G), \dots, con(ma_k,o,\ell,\Gamma,f,G)
%        \\%

%     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G) 
%        & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
%        &   & \textbf{else}~ n_1 : ( con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (con({ns}_2,\ell,\Gamma,f,G),n_3)%

%        \\
%     con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G) 
%        & = &  
%        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
%        \\
%\end{array} \]

### 2016-11-08 paper/abstraction/paper.tex
add formal definitions

Foo

>>>>

\newcommand{\Con}{\text{con}}

\vspace{2em}
\begin{figure*}[t!]\small

  \hrulefill%
  \vspace{1em}

  \begin{minipage}[t]{.46\linewidth}
  \hdr{ABGP Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     ma   &::=& n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3) & \textit{match action} \\
     ps   &::=& \{ t_1, ~\dots,~ t_k \} & \textit{predicates} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
  \end{array} \]%

  \end{minipage}
  %
  %
  \begin{minipage}[t]{.5\linewidth}
  \hdr{Compilation}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k) ) = \\
     ~~~~~ \{ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
     \\
     \text{compile}( p_1, \dots, p_k ) = \\
     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1), \dots, \text{compile}_\text{PG}(p_k)) \\
  \end{array} \]%
  \end{minipage}

  \vspace{1em}
  \vspace{1em}

  \vspace*{-2\baselineskip}
  \begin{minipage}[t]{\linewidth}
  \hdr{Policy Concretization}{}
  \vspace*{-2\baselineskip}
  %
  \[ \begin{array}{lcl}
     \\
     \Con(\emptyset, \Gamma, f)      &=& \emptyset \\
     \Con(l, \Gamma, f)              &=& \Sigma ~ f^{-1}(l) \\
     \Con(r_1 \cup r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cup \Con(r_2,\Gamma,f) \\
     \Con(r_1 \cap r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cap \Con(r_2,\Gamma,f) \\
     \Con(!r, \Gamma, f)             &=& !\Con(r,\Gamma,f) \\
     \Con(r^*, \Gamma, f)            &=& \Con(r,\Gamma,f)^* \\

     \Con(pfx ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=& 
          pfx ~\Path~ \Con(r_1,\Gamma,f), ~\dots~, \Con(r_k,\Gamma,f)  \\

     \Con(\$x ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&

         \{ pfx ~\Path~ \Con(r_1,\Gamma,f) \cap \text{end}(l), ~\dots~,
           \Con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \}  \\

     \Con(p_1, \dots, p_n, \Gamma,f) &=& \Con(p_1, \Gamma,f), \dots, \Con(p_n, \Gamma,f) \\

  \end{array} \]%
  \end{minipage}

  \vspace{1em}
  \vspace{1em}

  \begin{minipage}[t]{\linewidth}
  \hdr{ABGP Concretization}{}
  \vspace*{-2\baselineskip}
  %
  \[ \begin{array}{lcl}
     \\
     \Con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G) 
        & = & 
        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
        \\
     \Con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G) 
        & = &  
        \Con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, \Con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
        \\
     \Con(pfx \rightarrow {pc},\ell,\Gamma,f,G) 
        & = &  
        pfx \rightarrow \Con(pc,\text{true},\ell,\Gamma,f,G)
        \\
     \Con(\$x \rightarrow {pc},\ell,\Gamma,f,G) 
        & = &  
        \{ pfx \rightarrow \Con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
        \\
     \Con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G) 
        & = &
        \Con(ma_1,o,\ell,\Gamma,f,G), \dots, \Con(ma_k,o,\ell,\Gamma,f,G)
        \\

     \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G) 
        & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
        &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)

        \\
     \Con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G) 
        & = &  
        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
        \\
  \end{array} \]%
  \end{minipage}

  \vspace{1em}
  \hrulefill%
  \vspace{1em}

  \caption{ABGP syntax (a), compilation from product graphs (b), Policy concretization (c), and ABGP concretization (d).}
  \label{fig:abgp-syntax}

\end{figure*}%
